Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
sample 5000 points for dispersion dispersal plot

```{r}
disp_df %>%
  group_by(., model) %>%
  sample_n(., 1000) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  sample_n(., 1000) %>%
  ggplot(., aes(y = av.disp, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersal

>>>>

```{r}
disp_df %>%
  group_by(., model) %>%
  sample_n(., 5000) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  sample_n(., 5000) %>%
  ggplot(., aes(y = av.disp, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersal
